|

### 2023-07-17 paper/05-discussion.Rmd
Update discussion on rapm model with sabin reference (#12)

Through multilevel modeling, we observe that the pass rusher explains more variation in play-level STRAIN, followed by the quarterback and then their assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure.
However, we ignore the fact that pass rushers can be teammates cooperating in the same play leading to some type of correlation structure in their STRAIN values.
One way to address this complication could be with a adjusted plus-minus (APM) regression approach [@matano2023augmenting], with all players accounted for in modeling a total STRAIN quantity.

@@

Moreover, although we focus solely on pass rushers in this paper, STRAIN can also be applied to the assessment of pass blockers as a unit.
This can be accomplished through the aforementioned APM regression or by simply looking at quantities such as the total STRAIN or the maximum STRAIN per frame aggregated across the entire play.
It is also possible to apply STRAIN to assess individual offensive pass blockers, provided that a method of matching blockers to rushers was developed.
Furthermore, compared to existing metrics, STRAIN measures pass rush effectiveness for every play continuously over time, which is at a much more granular level than considering whether the play resulted in a binary outcome such as a sack.
There is ample opportunity for working with the complete STRAIN trajectories via functional data analysis to better understand the impact of STRAIN on offensive production in American football.

>>>>

Through multilevel modeling, we observe that the pass rusher explains more variation in play-level STRAIN, followed by the possession team, the pass rushing team, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure. However, our model is limited in that we only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects. The nested structure of our model enforces positive dependence between pass rushers on the same team, which may or may not be true. For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. This could leave the path open for another player to rush the quarterback with ease, leading to high STRAIN values. In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach. The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models. We leave this type of analysis for future work, which will require careful consideration of informative prior information [@matano2023augmenting].

@@

Moreover, although we focus solely on pass rushers in this paper, STRAIN can also be applied to the assessment of pass blockers as a unit.
This can be accomplished through the aforementioned RAPM regression or by simply looking at quantities such as the total STRAIN or the maximum STRAIN per frame aggregated across the entire play.
It is also possible to apply STRAIN to assess individual offensive pass blockers, provided that a method of matching blockers to rushers was developed.
Furthermore, compared to existing metrics, STRAIN measures pass rush effectiveness for every play continuously over time, which is at a much more granular level than considering whether the play resulted in a binary outcome such as a sack.
There is ample opportunity for working with the complete STRAIN trajectories via functional data analysis to better understand the impact of STRAIN on offensive production in American football.
